---
title: "New Checks"
author: "Francesca Micocci"
date: "7/7/2021"
output: html_document
---
# Libraries
```{r libraries,message=FALSE,warning=FALSE}
library(foreign)
library(haven)
library(reshape2)
library(ggplot2)
library(caret)
library(knitr)
library(kableExtra)
library(PRROC)
library(sf)
library(tmap)
library(scales)
library(viridis)
```

# Cut-off

Generate Sensitivity and Specificity at different probability thresholds. Then show graphically the optimalcutoff,i.e. the point where the Sensitivity and Specificity curves intercept.

1. Upload the data

```{r upload files}
rm(list=ls())
setwd('/your/directory/')
load("Export_project/Data/results.RData")
load("Export_project/Data/results_no_na.RData")
```

2. Merge the prediction results in a single dataset

```{r all pred}
final<-merge(results[,c("bvdidnumber","year","export","bart_mia_prob")],results_no_na[,c("bvdidnumber","year","export","logit.prob","rf.prob","bart.prob","lasso.prob")],by=c("bvdidnumber","year","export"),all.x = TRUE, all.y = TRUE)
rm(results_no_na)
```

3. Generate the sensitivity/specificity graphs by cutoffs.

## BART-MIA
Generate a sequence of 100 probability cutoff, each corresponding to an additional predicted probability of 0.01. Then generate a table reporting for each of these probability cutoffs the corresponding Sensitivity and Specificity.

```{r bart_mia}
cutoffs<-data.frame(matrix(vector(), 99, 3,
                dimnames=list(c(), c("cutoff","Sensitivity", "Specificity"))),
                stringsAsFactors=F)
cutoff_ls<-seq(0.01,1,0.01)
for (i in 1:99){
  predictions<-ifelse(final$bart_mia_prob>cutoff_ls[i],1,0)
  tab<-table(predictions,final$export)
  sensitivity<-tab[2,2]/(tab[2,2]+tab[1,2])
  specificity<-tab[1,1]/(tab[1,1]+tab[2,1])
  cutoffs[i,1]<-cutoff_ls[i]
  cutoffs[i,2]<-sensitivity
  cutoffs[i,3]<-specificity
}

cutoffs$BACC<-(cutoffs$Sensitivity+cutoffs$Specificity)/2
bart_mia <- melt(cutoffs, id.vars = c("cutoff"))
```

Plot the Sensitivity and Specificity graphs. 

```{r bart_mia graph}
ggplot(bart_mia,aes(x=cutoff,y=value,color=variable))+geom_point()+theme_bw()+labs(y= "Sensitivity/Specificity", x = "Probability cut-off",colour = " ",size=0.1) 
```

## BART
```{r bart}
cutoffs<-data.frame(matrix(vector(), 99, 3,
                dimnames=list(c(), c("cutoff","Sensitivity", "Specificity"))),
                stringsAsFactors=F)
cutoff_ls<-seq(0.01,1,0.01)
for (i in 1:99){
  predictions<-ifelse(final$bart.prob>cutoff_ls[i],1,0)
  tab<-table(predictions,final$export)
  sensitivity<-tab[2,2]/(tab[2,2]+tab[1,2])
  specificity<-tab[1,1]/(tab[1,1]+tab[2,1])
  cutoffs[i,1]<-cutoff_ls[i]
  cutoffs[i,2]<-sensitivity
  cutoffs[i,3]<-specificity
}

cutoffs$BACC<-(cutoffs$Sensitivity+cutoffs$Specificity)/2
bart <- melt(cutoffs, id.vars = c("cutoff"))
```
plot the Sensitivity and Specificity graphs at different probability thresholds
```{r bart graph}
ggplot(bart,aes(x=cutoff,y=value,color=variable))+geom_point()+theme_bw()+labs(y= "Sensitivity/Specificity", x = "Probability cut-off",colour = " ",size=0.2) 
```

## Random Forest
```{r RF, message=FALSE, warning=FALSE}
cutoffs<-data.frame(matrix(vector(), 99, 3,
                dimnames=list(c(), c("cutoff","Sensitivity", "Specificity"))),
                stringsAsFactors=F)
cutoff_ls<-seq(0.01,1,0.01)
for (i in 1:98){
  predictions<-ifelse(final$rf.prob>cutoff_ls[i],1,0)
  tab<-table(predictions,final$export)
  sensitivity<-tab[2,2]/(tab[2,2]+tab[1,2])
  specificity<-tab[1,1]/(tab[1,1]+tab[2,1])
  cutoffs[i,1]<-cutoff_ls[i]
  cutoffs[i,2]<-sensitivity
  cutoffs[i,3]<-specificity
}
cutoffs$BACC<-(cutoffs$Sensitivity+cutoffs$Specificity)/2
rf <- melt(cutoffs, id.vars = c("cutoff"))
```
plot the Sensitivity and Specificity graphs at different probability threshold
```{r RF graph, warning=FALSE,message=FALSE}
ggplot(rf,aes(x=cutoff,y=value,color=variable))+geom_point()+theme_bw()+labs(y= "Sensitivity/Specificity", x = "Probability cut-off",colour = " ",size=0.2) 
```

## Lasso
```{r lasso}
cutoffs<-data.frame(matrix(vector(), 99, 3,
                dimnames=list(c(), c("cutoff","Sensitivity", "Specificity"))),
                stringsAsFactors=F)
cutoff_ls<-seq(0.01,1,0.01)
for (i in 1:99){
  predictions<-ifelse(final$lasso.prob>cutoff_ls[i],1,0)
  tab<-table(predictions,final$export)
  sensitivity<-tab[2,2]/(tab[2,2]+tab[1,2])
  specificity<-tab[1,1]/(tab[1,1]+tab[2,1])
  cutoffs[i,1]<-cutoff_ls[i]
  cutoffs[i,2]<-sensitivity
  cutoffs[i,3]<-specificity
}

cutoffs$BACC<-(cutoffs$Sensitivity+cutoffs$Specificity)/2
lasso <- melt(cutoffs, id.vars = c("cutoff"))
```
plot the Sensitivity and Specificity graphs at different probability threshols
```{r lasso graph}
ggplot(lasso,aes(x=cutoff,y=value,color=variable))+geom_point()+theme_bw()+labs(y= "Sensitivity/Specificity", x = "Probability cut-off",colour = " ",size=0.2) 
```

## Logit
```{r logit}
cutoffs<-data.frame(matrix(vector(), 99, 3,
                dimnames=list(c(), c("cutoff","Sensitivity", "Specificity"))),
                stringsAsFactors=F)
cutoff_ls<-seq(0.01,1,0.01)
for (i in 1:99){
  predictions<-ifelse(final$logit.prob>cutoff_ls[i],1,0)
  tab<-table(predictions,final$export)
  sensitivity<-tab[2,2]/(tab[2,2]+tab[1,2])
  specificity<-tab[1,1]/(tab[1,1]+tab[2,1])
  cutoffs[i,1]<-cutoff_ls[i]
  cutoffs[i,2]<-sensitivity
  cutoffs[i,3]<-specificity
}

cutoffs$BACC<-(cutoffs$Sensitivity+cutoffs$Specificity)/2
logit <- melt(cutoffs, id.vars = c("cutoff"))
```
plot the Sensitivity and Specificity graphs at different probability threshols
```{r logit graph}
ggplot(logit,aes(x=cutoff,y=value,color=variable))+geom_point()+theme_bw()+labs(y= "Sensitivity/Specificity", x = "Probability cut-off",colour = " ",size=0.2 ) 
```

## Export data

Now export the data with the predicted probabilities of the algorithms,to be used in stata to compute the optimal cut-off for export status prediction.
```{r export data}
write.dta(final, "Export_project/Data/final.dta")
```

Use the cutoffs obtained in Stata to predict the export status of firms. Note that we will have a different optimal cutoff for each different algorithm. This kind of approach is useful to evaluate the final performance of the models. Note indeed, that the displayed Sensitivity and Specificity are the optimal ones for each model and this allows to compare such statistics across models.

```{r import cutoffs}
#Upload the data
final<-haven::read_dta("Export_project/Data/final_cutoffs.dta")
#generate the datasets of the performance statisatics
Stats_cutoff<-data.frame(matrix(vector(), 5, 7,
                dimnames=list(c(), c("Model","Sensitivity","Specificity","Balanced Accuracy","ROC","PR","Optimal Cut-off"))),
                stringsAsFactors=F)

#BART-MIA
predictions<-ifelse(final$bart_mia_prob>final$bart_mia_cutoff,1,0)
cm1=confusionMatrix(data = factor(predictions,levels=c("1","0")),
                reference = factor(final$export,levels=c("1","0")),positive="1")

roc.cutoff<-roc.curve(scores.class0 =as.numeric(final$bart_mia_prob),
                     weights.class0 = as.numeric(final$export),
                     curve = T)

pr.cutoff<-pr.curve(scores.class0 =as.numeric(final$bart_mia_prob),
                     weights.class0 = as.numeric(final$export),
                     curve = T)
roc_BART_MIA=as.data.frame(roc.cutoff$curve)
pr_BART_MIA=as.data.frame(pr.cutoff$curve)
Stats_cutoff[1,1]="BART-MIA"
Stats_cutoff[1,2]=cm1[["byClass"]][["Sensitivity"]]
Stats_cutoff[1,3]=cm1[["byClass"]][["Specificity"]]
Stats_cutoff[1,4]=cm1[["byClass"]][["Balanced Accuracy"]]
Stats_cutoff[1,5]=roc.cutoff[["auc"]]
Stats_cutoff[1,6]=pr.cutoff[["auc.integral"]]
Stats_cutoff[1,7]=median(final$bart_mia_cutoff)
#BART
final2<-na.omit(final)
predictions<-ifelse(final2$bart_prob>final2$bart_cutoff,1,0)
cm1=confusionMatrix(data = factor(predictions,levels=c("1","0")),
                reference = factor(final2$export,levels=c("1","0")),positive="1")

roc.cutoff<-roc.curve(scores.class0 =as.numeric(final2$bart_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
pr.cutoff<-pr.curve(scores.class0 =as.numeric(final2$bart_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
roc_BART=as.data.frame(roc.cutoff$curve)
pr_BART=as.data.frame(pr.cutoff$curve)
Stats_cutoff[2,1]="BART"
Stats_cutoff[2,2]=cm1[["byClass"]][["Sensitivity"]]
Stats_cutoff[2,3]=cm1[["byClass"]][["Specificity"]]
Stats_cutoff[2,4]=cm1[["byClass"]][["Balanced Accuracy"]]
Stats_cutoff[2,5]=roc.cutoff[["auc"]]
Stats_cutoff[2,6]=pr.cutoff[["auc.integral"]]
Stats_cutoff[2,7]=median(final2$bart_cutoff)
#Random Forest
predictions<-ifelse(final2$rf_prob>final2$rf_cutoff,1,0)
cm1=confusionMatrix(data = factor(predictions,levels=c("1","0")),
                reference = factor(final2$export,levels=c("1","0")),positive="1")

roc.cutoff<-roc.curve(scores.class0 =as.numeric(final2$rf_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
pr.cutoff<-pr.curve(scores.class0 =as.numeric(final2$rf_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
roc_RF=as.data.frame(roc.cutoff$curve)
pr_RF=as.data.frame(pr.cutoff$curve)
Stats_cutoff[3,1]="Random Forest"
Stats_cutoff[3,2]=cm1[["byClass"]][["Sensitivity"]]
Stats_cutoff[3,3]=cm1[["byClass"]][["Specificity"]]
Stats_cutoff[3,4]=cm1[["byClass"]][["Balanced Accuracy"]]
Stats_cutoff[3,5]=roc.cutoff[["auc"]]
Stats_cutoff[3,6]=pr.cutoff[["auc.integral"]]
Stats_cutoff[3,7]=median(final2$rf_cutoff)
#Lasso
predictions<-ifelse(final2$lasso_prob>final2$lasso_cutoff,1,0)
cm1=confusionMatrix(data = factor(predictions,levels=c("1","0")),
                reference = factor(final2$export,levels=c("1","0")),positive="1")

roc.cutoff<-roc.curve(scores.class0 =as.numeric(final2$lasso_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
pr.cutoff<-pr.curve(scores.class0 =as.numeric(final2$lasso_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
roc_lasso=as.data.frame(roc.cutoff$curve)
pr_lasso=as.data.frame(pr.cutoff$curve)
Stats_cutoff[4,1]="Lasso"
Stats_cutoff[4,2]=cm1[["byClass"]][["Sensitivity"]]
Stats_cutoff[4,3]=cm1[["byClass"]][["Specificity"]]
Stats_cutoff[4,4]=cm1[["byClass"]][["Balanced Accuracy"]]
Stats_cutoff[4,5]=roc.cutoff[["auc"]]
Stats_cutoff[4,6]=pr.cutoff[["auc.integral"]]
Stats_cutoff[4,7]=median(final2$lasso_cutoff)
#Logit
predictions<-ifelse(final2$logit_prob>final2$logit_cutoff,1,0)
cm1=confusionMatrix(data = factor(predictions,levels=c("1","0")),
                reference = factor(final2$export,levels=c("1","0")),positive="1")

roc.cutoff<-roc.curve(scores.class0 =as.numeric(final2$logit_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
pr.cutoff<-pr.curve(scores.class0 =as.numeric(final2$logit_prob),
                     weights.class0 = as.numeric(final2$export),
                     curve = T)
roc_logit=as.data.frame(roc.cutoff$curve)
pr_logit=as.data.frame(pr.cutoff$curve)
Stats_cutoff[5,1]="Logit"
Stats_cutoff[5,2]=cm1[["byClass"]][["Sensitivity"]]
Stats_cutoff[5,3]=cm1[["byClass"]][["Specificity"]]
Stats_cutoff[5,4]=cm1[["byClass"]][["Balanced Accuracy"]]
Stats_cutoff[5,5]=roc.cutoff[["auc"]]
Stats_cutoff[5,6]=pr.cutoff[["auc.integral"]]
Stats_cutoff[5,7]=median(final2$logit_cutoff)


for (i in 1:5){
  for (j in 2:7){
    Stats_cutoff[i,j]<-as.numeric(Stats_cutoff[i,j])
  }
}

```
**See the results**:Note that once we selected the optimal cut-off, instead of a generic 0.5, we see that BART-MIA performs better that the other algorithms in all indexed but Precision-Recall. 
```{r pcts final stats}
Stats_cutoff%>%
  knitr::kable(digits = 4,row.names=FALSE,format.args = list(big.mark = ","))%>%
  kableExtra::kable_classic(full_width = F,html_font = "Cambria")
```
# Generate ROC and PR pics
```{r}
theme_no_axes <- function(base.theme = theme_bw()) {
  base.theme %+replace%
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank()
    )
}
```

## Names
```{r}
#Names
BART=ggplot() +                      
  annotate("text",x = 1,y = 1,size = 13,
           label = "BART")+ theme_no_axes(theme_grey())
BART_MIA=ggplot() +                      # Draw ggplot2 plot with text only
  annotate("text",x = 1,y = 1,size = 10,
           label = "BART-MIA")+ theme_no_axes(theme_grey())
RF=ggplot() +                      # Draw ggplot2 plot with text only
  annotate("text",x = 1,y = 1,size = 13,
           label = "Random \nForest")+ theme_no_axes(theme_grey())
lasso=ggplot() +                      # Draw ggplot2 plot with text only
  annotate("text",x = 1,y = 1,size = 13,
           label = "Logit \nLasso")+ theme_no_axes(theme_grey())
logit=ggplot() +                      # Draw ggplot2 plot with text only
  annotate("text",x = 1,y = 1,size = 13,
           label = "Logit")+ theme_no_axes(theme_grey())

```
## ROC
```{r}
#ROC
roc.BART=ggplot(roc_BART, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
 guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("FPR")+ylab("Sensitivity")+
  labs(title=paste("\n ROC curve \n AUC=",round(Stats_cutoff[2,5],4),sep=""))+
  theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

roc.BART_MIA=ggplot(roc_BART_MIA, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
 guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("FPR")+ylab("Sensitivity")+
  labs(title=paste("\n ROC curve \n AUC=",round(Stats_cutoff[1,5],4),sep=""))+
  theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

roc.RF=ggplot(roc_RF, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
 guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("FPR")+ylab("Sensitivity")+
  labs(title=paste("\n ROC curve \n AUC=",round(Stats_cutoff[3,5],4),sep=""))+
 theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))


roc.lasso=ggplot(roc_lasso, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("FPR")+ylab("Sensitivity")+
  labs(title=paste("\n ROC curve \n AUC=",round(Stats_cutoff[4,5],4),sep=""))+
 theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))



roc.logit=ggplot(roc_logit, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("FPR")+ylab("Sensitivity")+
  labs(title=paste("\n ROC curve \n AUC=",round(Stats_cutoff[5,5],4),sep=""))+
 theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

```
## PR
```{r}
pr.BART=ggplot(pr_BART, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("Recall")+ylab("Precision")+
  labs(title=paste("ROC curve \n AUC=",round(Stats_cutoff[5,5],4),sep=""))+
  theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

pr.BART_MIA=ggplot(pr_BART_MIA, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("Recall")+ylab("Precision")+
  labs(title=paste("ROC curve \n AUC=",round(Stats_cutoff[5,5],4),sep=""))+
 theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

pr.RF=ggplot(pr_RF, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("Recall")+ylab("Precision")+
  labs(title=paste("ROC curve \n AUC=",round(Stats_cutoff[5,5],4),sep=""))+
 theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

pr.lasso=ggplot(pr_lasso, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("Recall")+ylab("Precision")+
  labs(title=paste("ROC curve \n AUC=",round(Stats_cutoff[5,5],4),sep=""))+
  theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))

pr.logit=ggplot(pr_logit, aes(x=V1, y=V2,color=V3)) +geom_point()+scale_colour_gradientn(name="",colors=rainbow(7),limits = c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1))+
guides(colour = guide_colourbar(label.theme = element_text(angle = 90,size=12),barheight =20,barwidth = 0.8))+
  xlab("Recall")+ylab("Precision")+
  labs(title=paste("ROC curve \n AUC=",round(Stats_cutoff[5,5],4),sep=""))+
  theme(plot.title = element_text(hjust = 0.5,size=16,face='bold'),
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=1))



```

```{r}
library("ggpubr")
library(ggplot2)
library(gridExtra)
library(grid)
plot.list=list(logit,roc.logit,pr.logit,lasso,roc.lasso,pr.lasso,RF,roc.RF,pr.RF,BART,roc.BART,pr.BART,BART_MIA,roc.BART_MIA,pr.BART_MIA)
tiff(filename="tiff_pic/ROC_PR.tiff",units="px",width=1400, height=2000)
ggarrange(plotlist = plot.list,ncol = 3,
  nrow = 5,widths = c(0.3, 1,1))
dev.off()

png(filename="/Users/francescamicocci/Desktop/tiff_pic/ROC_PR.png",units="px",width=1400, height=2000)
ggarrange(plotlist = plot.list,ncol = 3,
  nrow = 5,widths = c(0.3, 1,1))
dev.off()

```


clear the environment
```{r clean}
rm(cm1,cutoffs,final2,pr.cutoff,roc.cutoff,cutoff_ls,i,j,sensitivity,specificity,tab,predictions)
```

