---
title: "BART-MIA"
author: "Francesca Micocci"
date: "6/26/2021"
output: html_document
---
# Import 

Import the required libraries
```{r libraries}
library(caret)
library(PRROC)
library(tidyverse)
library(stringr)
```

Import data
```{r import data}
load('/Users/francescamicocci/Documents/Export_project/Data/data_for_ML_BART_MIA.RData')
```

# BART-MIA
For BART-MIA we have to include missing information. As a result, we need to generate new train and test sets on the dataset including missing values. However, we want to avoid to include firms with all missing financial accounts, as a result, we will drop those firms presenting NAs in more that 42 variables over the 55 total (42 corresponds to the number of original financial accounts present on our predictors) 

1. Subset the original data to be used for ML, dropping the obs with too many NA
2. Generate the list of firms present in the subsetted data
3. Generate the 5 random samples of firms to be used for testing (each set contains $20\%$ of total firms)
4. Generate the corresponding 5 sets of firms to be used for training (each set contains $80\%$ of total firms)


```{r train and test}
#Generate a variable counting the number of NA by row
data_ML.n$missing<-rowSums(is.na(data_ML.n))
#Drop obs with more than 42 NA
data_ML.m<-subset(data_ML.n,data_ML.n$missing<42)
#Generate the list of firms
firms.m <- as.vector(data_ML.m[!duplicated(data_ML.m$bvdidnumber),]$bvdidnumber)
#Sample the firms
set.seed(2002)
ss <- sample(1:5,size=length(firms.m),replace=TRUE,prob=c(0.2,0.2,0.2,0.2,0.2))
firms<-as.data.frame(cbind(firms.m,ss))
testing_firms_1  <- firms[firms$ss==1,]$firms.m
testing_firms_2  <- firms[firms$ss==2,]$firms.m
testing_firms_3  <- firms[firms$ss==3,]$firms.m
testing_firms_4  <- firms[firms$ss==4,]$firms.m
testing_firms_5  <- firms[firms$ss==5,]$firms.m
#generate the testing firms, as complement of training firms to total firms
training_firms_1<-setdiff(firms$firms,testing_firms_1)
training_firms_2<-setdiff(firms$firms,testing_firms_2)
training_firms_3<-setdiff(firms$firms,testing_firms_3)
training_firms_4<-setdiff(firms$firms,testing_firms_4)
training_firms_5<-setdiff(firms$firms,testing_firms_5)

#Generate the 5 train and test set subsetting by bvdid in the list of training and testing set respectively

train1.m<-subset(data_ML.m, bvdidnumber %in% training_firms_1)
test1.m<-subset(data_ML.m, bvdidnumber %in% testing_firms_1)

train2.m<-subset(data_ML.m, bvdidnumber %in% training_firms_2)
test2.m<-subset(data_ML.m, bvdidnumber %in% testing_firms_2)

train3.m<-subset(data_ML.m, bvdidnumber %in% training_firms_3)
test3.m<-subset(data_ML.m, bvdidnumber %in% testing_firms_3)

train4.m<-subset(data_ML.m, bvdidnumber %in% training_firms_4)
test4.m<-subset(data_ML.m, bvdidnumber %in% testing_firms_4)

train5.m<-subset(data_ML.m, bvdidnumber %in% training_firms_5)
test5.m<-subset(data_ML.m, bvdidnumber %in% testing_firms_5)
#remove useless stuff

rm(ss,firms,training_firms_1,training_firms_2,training_firms_3,training_firms_4,training_firms_5,testing_firms_1,testing_firms_2,testing_firms_3,testing_firms_4,testing_firms_5)
```
Export the training data to be used. Upload it on terminal. Proceed with the algorithms on the Server. Download the Data back to local. Keep with usual stuff

Save data to be used locally.
```{r save train test}
save(train1.m,file= "/Users/francescamicocci/Documents/Export_project/Data/train1.m.RData")
save(test1.m,file= "/Users/francescamicocci/Documents/Export_project/Data/test1.m.RData")
save(train2.m,file= "/Users/francescamicocci/Documents/Export_project/Data/train2.m.RData")
save(test2.m,file= "/Users/francescamicocci/Documents/Export_project/Data/test2.m.RData")
save(train3.m,file= "/Users/francescamicocci/Documents/Export_project/Data/train3.m.RData")
save(test3.m,file= "/Users/francescamicocci/Documents/Export_project/Data/test3.m.RData")
save(train4.m,file= "/Users/francescamicocci/Documents/Export_project/Data/train4.m.RData")
save(test4.m,file= "/Users/francescamicocci/Documents/Export_project/Data/test4.m.RData")
save(train5.m,file= "/Users/francescamicocci/Documents/Export_project/Data/train5.m.RData")
save(test5.m,file= "/Users/francescamicocci/Documents/Export_project/Data/test5.m.RData")
```
## SERVER!
Now open the Terminal and upload the file
```{}
scp /Users/francescamicocci/Documents/Export_project/Data/train1.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/test1.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/train2.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/test2.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/train3.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/test3.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/train4.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/test4.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/train5.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL

scp /Users/francescamicocci/Documents/Export_project/Data/test5.m.RData francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/
KQyVZQ9v3uL
```

For each Sample, open a new R session in a tmux environment, so as to be able to detach the Server session from the local connection. Then load the required libraries, run the model and predict the export probabilities on the test set. For the first sample, compute the variable importance plot, which reports the inclusion proportion of the features.

### Sample 1
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux new -s simul_nocov
R
library(rJava)
options(java.parameters="-Xmx150g")
library("bartMachine")

load("/home/francesca.micocci/Export_project/train1.m.RData")
load("/home/francesca.micocci/Export_project/test1.m.RData")

y <- factor(train1.m$export,levels=c("1","0"))
X<-as.data.frame(train1.m)
X$export<-NULL
X$bvdidnumber<-NULL
X$year<-NULL
bart_machine.1<-bartMachine(X, y,use_missing_data=TRUE,use_missing_data_dummies_as_covars=TRUE,seed=2021)
test1.m$export<-NULL
test1.m$bvdidnumber<-NULL
test1.m$year<-NULL
bart_machine.fitted1.m<-predict(bart_machine.1, test1.m,type='prob')
save(bart_machine.fitted1.m,file="/home/francesca.micocci/Export_project/bart.fitted1.m.RData")

var.imp<-investigate_var_importance(bart_machine.1)
save(var.imp,file="/home/francesca.micocci/Export_project/var_imp.RData")
```
Detach the process from local computer
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux detach
```

### Sample 2
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux new -s bart_mia_2
R
library(rJava)
options(java.parameters="-Xmx150g")
library("bartMachine")

load("/home/francesca.micocci/Export_project/train2.m.RData")
load("/home/francesca.micocci/Export_project/test2.m.RData")

y <- factor(train2.m$export,levels=c("1","0"))
X<-as.data.frame(train2.m)
X$export<-NULL
X$bvdidnumber<-NULL
X$year<-NULL
bart_machine.2<-bartMachine(X, y,use_missing_data=TRUE,use_missing_data_dummies_as_covars=TRUE,seed=2021)
test2.m$export<-NULL
test2.m$bvdidnumber<-NULL
test2.m$year<-NULL
bart_machine.fitted2.m<-predict(bart_machine.2, test2.m,type='prob')
save(bart_machine.fitted2.m,file="/home/francesca.micocci/Export_project/bart.fitted2.m.RData")
```
Detach the process from local computer
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux detach
```
### Sample 3
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux new -s bart_mia_3
R
library(rJava)
options(java.parameters="-Xmx150g")
library("bartMachine")

load("/home/francesca.micocci/Export_project/train3.m.RData")
load("/home/francesca.micocci/Export_project/test3.m.RData")

y <- factor(train3.m$export,levels=c("1","0"))
X<-as.data.frame(train3.m)
X$export<-NULL
X$bvdidnumber<-NULL
X$year<-NULL
bart_machine.3<-bartMachine(X, y,use_missing_data=TRUE,use_missing_data_dummies_as_covars=TRUE)
test3.m$export<-NULL
test3.m$bvdidnumber<-NULL
test3.m$year<-NULL
bart_machine.fitted3.m<-predict(bart_machine.3, test3.m,type='prob')
save(bart_machine.fitted3.m,file="/home/francesca.micocci/Export_project/bart.fitted3.m.RData")
```

Detach the process from local computer
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux detach
```

### Sample 4
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux new -s bart_mia_4
R
library(rJava)
options(java.parameters="-Xmx150g")
library("bartMachine")

load("/home/francesca.micocci/Export_project/train4.m.RData")
load("/home/francesca.micocci/Export_project/test4.m.RData")

y <- factor(train4.m$export,levels=c("1","0"))
X<-as.data.frame(train4.m)
X$export<-NULL
X$bvdidnumber<-NULL
X$year<-NULL
bart_machine.4<-bartMachine(X, y,use_missing_data=TRUE,use_missing_data_dummies_as_covars=TRUE)
test4.m$export<-NULL
test4.m$bvdidnumber<-NULL
test4.m$year<-NULL
bart_machine.fitted4.m<-predict(bart_machine.4, test4.m,type='prob')
save(bart_machine.fitted4.m,file="/home/francesca.micocci/Export_project/bart.fitted4.m.RData")
```

Detach the process from local computer
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux detach
```

### Sample 5
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux new -s bart_mia_5
R
library(rJava)
options(java.parameters="-Xmx150g")
library("bartMachine")

load("/home/francesca.micocci/Export_project/train5.m.RData")
load("/home/francesca.micocci/Export_project/test5.m.RData")

y <- factor(train5.m$export,levels = c("1","0"))
X<-as.data.frame(train5.m)
X$export<-NULL
X$bvdidnumber<-NULL
X$year<-NULL
bart_machine.5<-bartMachine(X, y,use_missing_data=TRUE,use_missing_data_dummies_as_covars=TRUE)
test5.m$export<-NULL
test5.m$bvdidnumber<-NULL
test5.m$year<-NULL
bart_machine.fitted5.m<-predict(bart_machine.5, test5.m,type='prob')
save(bart_machine.fitted5.m,file="/home/francesca.micocci/Export_project/bart.fitted5.m.RData")

```

Detach the process from local computer
```{}
ssh francesca.micocci@10.181.100.119
KQyVZQ9v3uL

tmux detach
```

Download the results on local
```{}
scp francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/bart.fitted1.m.RData /Users/francescamicocci/Documents/Server/bart.fitted1.m.RData
KQyVZQ9v3uL

scp francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/bart.fitted2.m.RData /Users/francescamicocci/Documents/Server/bart.fitted2.m.RData
KQyVZQ9v3uL

scp francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/bart.fitted3.m.RData /Users/francescamicocci/Documents/Server/bart.fitted3.m.RData
KQyVZQ9v3uL

scp francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/bart.fitted4.m.RData /Users/francescamicocci/Documents/Server/bart.fitted4.m.RData
KQyVZQ9v3uL

scp francesca.micocci@10.181.100.119:/home/francesca.micocci/Export_project/bart.fitted5.m.RData /Users/francescamicocci/Documents/Server/bart.fitted5.m.RData
KQyVZQ9v3uL

scp francesca.micocci@10.181.100.119:/home/francesca.micocci/Customs/Completed/matrix_24_completed.RData /Users/francescamicocci/Documents/Server/completed_24.RData



```

## Evaluate BART-MIA
Now proceed with the predictions based on BART.
```{r load results}
load("/Users/francescamicocci/Documents/Server/bart.fitted1.m.RData")
load("/Users/francescamicocci/Documents/Server/bart.fitted2.m.RData")
load("/Users/francescamicocci/Documents/Server/bart.fitted3.m.RData")
load("/Users/francescamicocci/Documents/Server/bart.fitted4.m.RData")
load("/Users/francescamicocci/Documents/Server/bart.fitted5.m.RData")
```

Confusion Matrix
```{r confusionMatrix BART_MIA}
test1.m$bart_mia_prob=(bart_machine.fitted1.m)
test2.m$bart_mia_prob=(bart_machine.fitted2.m)
test3.m$bart_mia_prob=(bart_machine.fitted3.m)
test4.m$bart_mia_prob=(bart_machine.fitted4.m)
test5.m$bart_mia_prob=(bart_machine.fitted5.m)

rm(bart_machine.fitted1.m,bart_machine.fitted2.m,bart_machine.fitted3.m,bart_machine.fitted4.m,bart_machine.fitted5.m)

test1.m$bart_mia_pred<-ifelse(test1.m$bart_mia_prob>0.5,1,0)
test2.m$bart_mia_pred<-ifelse(test2.m$bart_mia_prob>0.5,1,0)
test3.m$bart_mia_pred<-ifelse(test3.m$bart_mia_prob>0.5,1,0)
test4.m$bart_mia_pred<-ifelse(test4.m$bart_mia_prob>0.5,1,0)
test5.m$bart_mia_pred<-ifelse(test5.m$bart_mia_prob>0.5,1,0)

cm1=confusionMatrix(data = factor(test1.m$bart_mia_pred,levels=c("1","0")),
                reference = factor(test1.m$export,levels=c("1","0")),positive = "1")

cm2=confusionMatrix(data = factor(test2.m$bart_mia_pred,levels=c("1","0")),
                reference = factor(test2.m$export,levels=c("1","0")),positive = "1")

cm3=confusionMatrix(data = factor(test3.m$bart_mia_pred,levels=c("1","0")),
                reference = factor(test3.m$export,levels=c("1","0")),positive = "1")

cm4=confusionMatrix(data = factor(test4.m$bart_mia_pred,levels=c("1","0")),
                    reference = factor(test4.m$export,levels=c("1","0")),positive = "1")

cm5=confusionMatrix(data = factor(test5.m$bart_mia_pred,levels=c("1","0")),
                reference = factor(test5.m$export,levels=c("1","0")),positive = "1")
```
Generate the summary statistics table
```{r BARRT_MIA stats}
Bart_MIA_Statistics<-data.frame(matrix(vector(), 4, 6,
                dimnames=list(c(), c("Performance.Measure", "Sample1", "Sample2","Sample3","Sample4","Sample5"))),
                stringsAsFactors=F)
Bart_MIA_Statistics$Performance.Measure<-c("Accuracy","Sensitivity","Specificity","Balanced Accuracy")

Bart_MIA_Statistics$Sample1<-c(cm1[["overall"]][["Accuracy"]],cm1[["byClass"]][["Sensitivity"]],cm1[["byClass"]][["Specificity"]],cm1[["byClass"]][["Balanced Accuracy"]])

Bart_MIA_Statistics$Sample2<-c(cm2[["overall"]][["Accuracy"]],cm2[["byClass"]][["Sensitivity"]],cm2[["byClass"]][["Specificity"]],cm2[["byClass"]][["Balanced Accuracy"]])

Bart_MIA_Statistics$Sample3<-c(cm3[["overall"]][["Accuracy"]],cm3[["byClass"]][["Sensitivity"]],cm3[["byClass"]][["Specificity"]],cm3[["byClass"]][["Balanced Accuracy"]])

Bart_MIA_Statistics$Sample4<-c(cm4[["overall"]][["Accuracy"]],cm4[["byClass"]][["Sensitivity"]],cm4[["byClass"]][["Specificity"]],cm4[["byClass"]][["Balanced Accuracy"]])

Bart_MIA_Statistics$Sample5<-c(cm5[["overall"]][["Accuracy"]],cm5[["byClass"]][["Sensitivity"]],cm5[["byClass"]][["Specificity"]],cm5[["byClass"]][["Balanced Accuracy"]])

rm(cm1,cm2,cm3,cm4,cm5)
```

ROC Curve
```{r ROC BART_MIA}
roc_BART1.m <- roc.curve(scores.class0 =as.numeric(test1.m$bart_mia_prob),
                     weights.class0 = as.numeric(test1.m$export),
                     curve = T)

roc_BART2.m <- roc.curve(scores.class0 =as.numeric(test2.m$bart_mia_prob),
                     weights.class0 = as.numeric(test2.m$export),
                     curve = T)

roc_BART3.m <- roc.curve(scores.class0 =as.numeric(test3.m$bart_mia_prob),
                     weights.class0 = as.numeric(test3.m$export),
                     curve = T)

roc_BART4.m <- roc.curve(scores.class0 =as.numeric(test4.m$bart_mia_prob),
                    weights.class0 = as.numeric(test4.m$export),
                    curve = T)

roc_BART5.m <- roc.curve(scores.class0=as.numeric(test5.m$bart_mia_prob),weights.class0=as.numeric(test5.m$export),
                    curve = T)

roc<-c("ROC",roc_BART1.m[["auc"]],roc_BART2.m[["auc"]],roc_BART3.m[["auc"]],roc_BART4.m[["auc"]],roc_BART5.m[["auc"]])

Bart_MIA_Statistics<-rbind(Bart_MIA_Statistics,roc)
rm(roc_BART1.m,roc_BART2.m,roc_BART3.m,roc_BART4.m,roc_BART5.m,roc)
```
PR Curve
```{r PR BART_MIA}
pr_BART1.m <- pr.curve(scores.class0 =as.numeric(test1.m$bart_mia_prob),
                     weights.class0 = as.numeric(test1.m$export),
                     curve = T)

pr_BART2.m <- pr.curve(scores.class0 =as.numeric(test2.m$bart_mia_prob),
                     weights.class0 = as.numeric(test2.m$export),
                     curve = T)

pr_BART3.m <- pr.curve(scores.class0 =as.numeric(test3.m$bart_mia_prob),
                     weights.class0 = as.numeric(test3.m$export),
                     curve = T)

pr_BART4.m <- pr.curve(scores.class0 =as.numeric(test4.m$bart_mia_prob),
                    weights.class0 = as.numeric(test4.m$export),
                    curve = T)

pr_BART5.m <- pr.curve(scores.class0 =as.numeric(test5.m$bart_mia_prob),
                     weights.class0 = as.numeric(test5.m$export),
                     curve = T)

pr<-c("PR",pr_BART1.m[["auc.integral"]],pr_BART2.m[["auc.integral"]],pr_BART3.m[["auc.integral"]],pr_BART4.m[["auc.integral"]],pr_BART5.m[["auc.integral"]])

Bart_MIA_Statistics<-rbind(Bart_MIA_Statistics,pr)
rm(pr_BART1.m,pr_BART2.m,pr_BART3.m,pr_BART4.m,pr_BART5.m,pr)

```
Add sample size and round the decimals
```{r Testing Size}
size_testing<-c("Size Sample",nrow(test1.m),nrow(test2.m),nrow(test3.m),nrow(test4.m),nrow(test5.m))
Bart_MIA_Statistics<-rbind(Bart_MIA_Statistics,size_testing)

Bart_MIA_Statistics[,c(2:6)] <- sapply(Bart_MIA_Statistics[,c(2:6)],as.numeric)
Bart_MIA_Statistics=Bart_MIA_Statistics %>% mutate_if(is.numeric, ~round(., 3))
```
See the results:
```{r BART_MIA stats final}
Bart_MIA_Statistics%>%
  knitr::kable(digits = 4) %>%
  kableExtra::kable_paper("hover", full_width = T)
```
## ROC and PR Graphs
```{r roc pr graph}
roc_BART_MIA<- roc.curve(scores.class0 =as.numeric(test1.m$bart_mia_prob),
                     weights.class0 = as.numeric(test1.m$export),
                     curve = T)

pr_BART_MIA<- pr.curve(scores.class0 =as.numeric(test1.m$bart_mia_prob),
                     weights.class0 = as.numeric(test1.m$export),
                     curve = T)

plot(roc_BART_MIA)
plot(pr_BART_MIA)
```

# Generate data with BART-MIA predictions

Generate a variable counting the number of exporting years in the dataset *exporting_history*
```{r}
exporting_history$num_years<-str_count(exporting_history$export_shape,"1")
```

Now generate the data with all the predictions, and merge it with some relevant columns of the dataset exporting_history.

```{r}
results=rbind.data.frame(test1.m,test2.m,test3.m,test4.m,test5.m)
results=merge(results,exporting_history[,c("bvdidnumber","export_type","num_years")],by="bvdidnumber")
```

Export the dataset
```{r}
save(results,file="/Users/francescamicocci/Documents/Export_project/Data/results.RData")
```

