---
title: "Preliminary Analysis"
author: "Francesca Micocci"
date: "6/25/2021"
output: html_document
---

```{r setup, include=FALSE}
require("knitr")
knitr::opts_knit$set(root.dir ='/your/directory/Export_project/Data/')
```


Perform a preliminary analysis on the persistency of exporting activity. Then verify the relationship between export status and some variables which are traditionally correlated with exporting activity, e.g., **size**, **TFP**,**markups**,* **wage**. In particular, draw some graphs and run Welsch tests to check for the distribution of variables of interest in the population of exporters vs non-exporters

# Import 

Import the required libraries
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(scales)
library(ggpubr)
library(corrplot)
library(gridGraphics)
library(grid)
```

Import data obtained as output of Step1 on R

```{r}
setwd('your/directory/')
load('Export_project/Data/data_R.RData')
```
# Persistency of exporting activity

Check for the distribution of exporters in terms of _"number of years they exported, out of 9 possible"_. Then draw the graph.

```{r}
data_exp_int<-data[,c("bvdidnumber","export","past_exp_intensity","year")]
data_exp_int<-data_exp_int[data_exp_int$year==2018,]

exp_years<-as.data.frame(table(data_exp_int$past_exp_intensity))

ggplot(exp_years, aes(x=Var1, y=Freq)) +
      geom_bar(stat="identity")+labs(title="Number of firms by number of exporting years" ,
      x = "Number of years of exporting out of 9", y = "Number of firms")+
      theme_grey(base_size = 14)
```

# Export and firm characteristics

Start with TFP and markups. We expect Exporters to be more productive than non-exporters. in particular we expect exporters to have higher productivity and markups than non-exporters. Similarly we check for the difference in Log (Employment) and Wages between exporters and non-exporters. As for TFP and markuops, we expect exporters to be, on average, bigger and to pay higher salaries.

## TFP
```{r TFP graph,warning=FALSE, message=FALSE}
ggplot(data[which(!is.na(data$export)),], aes(x=TFP_acf, fill=as.factor(export))) +
      geom_density(alpha=.22)+labs(title="Total Factor Productivity density curve", 
      x = "Total Factor Productivity", y = "density", fill = "Export \ndummy\n") +
      theme_grey(base_size = 14)
```
```{r TFP test}
TFP.t.test <- t.test(TFP_acf ~ export, data = data)
TFP.t.test
```
## Markups
```{r markups plot,warning=FALSE, message=FALSE}
ggplot(data[which(!is.na(data$export)),], aes(x=markups, fill=as.factor(export))) +
      geom_density(alpha=.22)+labs(title="Markups density curve", x = "Markups", 
      y = "density", fill = "Export \ndummy\n") +theme_grey(base_size = 14)+
      coord_cartesian(xlim = c(-1, 26)) 
```

```{r markups test}
markups.test <- t.test(markups ~ export, data = data)
markups.test
```

## Size
```{r size plot,warning=FALSE, message=FALSE}
ggplot(data[which(!is.na(data$export)),], aes(x=log_emp, fill=as.factor(export)))+
        geom_density(alpha=.22)+labs(title="Employment size density curve" ,
        x = "Log(number of employees)", y = "density", fill = "Export\ndummy\n")+
        theme_grey(base_size = 14)
```
```{r size test}
size.t.test <- t.test(l ~ export, data = data)
size.t.test
```
## Wage
```{r wage plot,warning=FALSE, message=FALSE}
ggplot(data[which(!is.na(data$export)),], aes(x=wage, fill=as.factor(export))) +
      geom_density(alpha=.22)+labs(title="Hourly Wage density curve",x="Hourly Wage",
      fill = "Export \ndummy\n")+theme_grey(base_size = 14)
```
```{r wage test}
wage.t.test <- t.test(wage ~ export, data = data)
wage.t.test
```

# Plot exporters share by nace.

1. Generate a table of exporters and non-exporters by nace
2.  Rename the numeric variable nace_2d, to provide a short description of the corresponding Nace category

```{r}
export_by_nace<-as.data.frame(table(data$export, data$nace_2d))
export_by_nace$Nace<-ifelse(export_by_nace$Var2=="10","10: Food products",
ifelse(export_by_nace$Var2=="11","11: Beverages",
ifelse(export_by_nace$Var2=="12","12:Tobacco",
ifelse(export_by_nace$Var2=="13", "13: Textiles",
ifelse(export_by_nace$Var2=="14", "14: Wearing Apparel",  
ifelse(export_by_nace$Var2=="15", "15: Leather",
ifelse(export_by_nace$Var2=="16", "16: Wood",  
ifelse(export_by_nace$Var2=="17", "17: Paper", 
ifelse(export_by_nace$Var2=="18", "18: Printing", 
ifelse(export_by_nace$Var2=="19","19: Coke and refined petroleum", 
ifelse(export_by_nace$Var2=="20", "20: Chemicals", 
ifelse(export_by_nace$Var2=="21", "21: Pharmaceutical prod", 
ifelse(export_by_nace$Var2=="22", "22: Rubber and Plastic",
ifelse(export_by_nace$Var2=="23", "23: Non-metallic mineral product",  
ifelse(export_by_nace$Var2=="24", "24: Basic metals", 
ifelse(export_by_nace$Var2=="25", "25: Fabricated metals", 
ifelse(export_by_nace$Var2=="26", "26: Computer, electronic and optical prod",
ifelse(export_by_nace$Var2=="27", "27: Electrical equipment", 
ifelse(export_by_nace$Var2=="28", "28: Machinery and equipment n.e.c.", 
ifelse(export_by_nace$Var2=="29", "29: Motor vehicles",
ifelse(export_by_nace$Var2=="30", "30: Other transportation",
ifelse(export_by_nace$Var2=="31", "31: Furniture",
"32: Other manifacturing"))))))))))))))))))))))
export_by_nace<-export_by_nace[export_by_nace$Var2!="12",]

```

3.  generate a barplot, reporting the number of observations

```{r}
ggplot(export_by_nace, aes( fill=Var1, y=Freq, x=Nace,na.rm = TRUE)) + 
  coord_flip()+geom_col(position="dodge") +
  labs(title = "Exporters and Non-exporters by Nace rev.2", y = "Count", x = "Nace Rev.2",fill="Export Dummy")+theme_bw()+theme(legend.position="bottom")+scale_y_continuous(labels = comma_format(big.mark = ".",
                                           decimal.mark = ","))+geom_text(aes(label = round(Freq, 1)),position = position_dodge(0.95),vjust = 0.5,hjust = -0.2,size=2)+ expand_limits(y = 140000)
```

# Correlation matrix of predictors

As a first step keep only numeric variables. Then draw the correlation matrix.

```{r, results='hide',fig.show='hide'}
#Generate the index of the numeric variables
numeric_var<-unlist(lapply(data_ML.n, is.numeric))  
# Keep only numeric variables
for_corr_matrix<-data_ML.n[,numeric_var]
# Drop year and output
for_corr_matrix<-subset(for_corr_matrix,select=-c(year,export))
# Order the predictors alphabetically
for_corr_matrix<-for_corr_matrix[,order(colnames(for_corr_matrix))]

# Generate a list of the variable names
col_names<-c("added value","age","capital adequacy ratio","capital intensity","cash and cash equiv.","cash flow","creditors","current assets","current liabilities","current ratio","debtors","deprec. and amort.","EBITDA","external econ. of scale","financial constraints","financial sustainability","financial expenses","financial revenue","fixed assets","ICR","intangible fixed assets","interest paid","labour productivity","liquidity returns","liquidity ratio","loans","size","long-term debt","markups","material costs","non-current liab","oper. revenue turn.","productive capacity","profitability","shareholders funds","size-age","solvency ratio","industrial spillovers","regional spillovers","tangible fixed ass.","taxation","TFP ACF","total assets","wage","working capital")
#Generate short names to be used in the graph
new_names<-paste("V",1:length(col_names),sep="")
# Rename the columns on the table 
colnames(for_corr_matrix) <- new_names

#Generate the correlation matrix
#testRes = cor.mtest(for_corr_matrix,use = "complete.obs",conf.level = 0.95)
res <- cor(for_corr_matrix,use = "complete.obs")
#Generate a vector to be used for the legend
new_names2=paste(new_names,": ",sep="")

#Generate the table to be put in the legend
labels2<-cbind.data.frame(new_names2[1:23],col_names[1:23],c(new_names2[24:45]," "),c(col_names[24:45]," "),stringsAsFactors = F)
#Drop colnames
colnames(labels2)<-c(" "," "," "," ")
# Generate the gg table
labels.p <- ggtexttable(labels2, rows = NULL, 
                        theme=ttheme(
              colnames.style = colnames_style(color = "black", fill = "white",hjust=0,x=0.1),
              tbody.style = tbody_style(color = "black",fill=c("white","white","white","white"), hjust=0, x=0.1,size = 12)
            ))
  
# Put column 1 and 3 in Bold
for (i in 2:24){
  labels.p <-table_cell_font(labels.p, row = i, column = 1,
                             face= "bold",size=12)
}
for (i in 2:23){
  labels.p <-table_cell_font(labels.p, row = i, column = 3,
                             face= "bold",size=12)
}
labels.p=labels.p%>%tab_add_title(text = "Legend", face = "bold", size = 14)
# Generate the correlartion matrix
corrplot(res, tl.pos = "td", tl.cex = 0.7, method = "ellipse", type = "upper",tl.col = "black", mar = c(1, 1, 1, 1),asp=1)
#Store it in a grid obj
grid.echo()
P1 <- grid.grab()
#Generate the final picture
png("Export_project/Versione_finale/Fig2_Correlation_plot.png", width = 1200, height = 650,units="px")
ggarrange(NULL,P1,NULL,labels.p,
           widths = c(-0.15,1, -0.25, 0.5), nrow = 1)
dev.off()
```
```{r}
#Generate the final picture
tiff("Export_project/Versione_finale/corrplot.tiff", width = 1000, height = 550,units="px")
ggarrange(NULL,P1,NULL,labels.p,
           widths = c(-0.15,1, -0.25, 0.5), nrow = 1)
dev.off()
```

